Beyond Adaptive Web Design

### 2014-03-16 paper/paper.tex
feat: reveal the attendance
feat: add tested web components

We have tracked amount of saved web traffic and web requests, webpage rendering time and interest in alternative input methods. We have also received a lot of feedback from the community which helped us to verify the proposed concept.

@@

We use the Mobile First principe so we make a default element static and pull in a static image. This approach saves a lot of web traffic and becasue of limited mobile data plans also user's money. We can then detect when it is appropriate to download the embedded map or to launch the native mobile application.

>>>>

We have tracked amount of saved web traffic and web requests, webpage rendering time and interest in alternative input methods. We have also received a lot of feedback from the community which helped us to verify the proposed concept. According to analytics the experiment has been attended by thousands of users and still has the weekly traffic one hundred of unique visitors.

@@

We have used the Mobile First principle to develop Google Maps and Youtube videos web components. So we make a default element static and pull in a static image. This approach saves a lot of web traffic and becasue of limited mobile data plans also user's money. We can then detect when it is appropriate to download the embedded map or to launch the native mobile application.
